High-order cognition is supported by information-rich but compressible brain activity patterns

### 2023-03-16 paper/main.tex
working on main text; almost done revising/updating

\newcommand{\topics}{S1}

@@

In addition to examining different networks in isolation, we wondered about the
general structure of the full-brain (i.e., potentially multi-network) activity
patterns reflected by different principal components across different
experimental conditions. As shown in Figure~\ref{fig:neurosynth-pca}, we used
Neurosynth~\citep{RubiEtal17} to identify, for each component, the associations
with each of 80 themes (see \textit{Reverse inference}).  In general, the first
principal components across all of the experimental conditions tended to weight
most heavily on themes related to cognitive control, memory,
language processing, attention, and perception.

To elucidate....\textbf{JRM STOPPED HERE}

We noticed (by
inspection) several common themes across the sets of terms associated with each
component and condition. Memory-related components included terms like ``middle
temporal,'' ``memory retrieval,'' and ``working memory.'' Sensory processing
related components included terms like ``primary visual,'' ``auditory cortex,''
``v1,'' and so on. Other components were associated with sensory integration
(e.g., ``thalamic,'' ``cingulate,'' etc.), sentence comprehension (e.g.,
``sentence,'' ``comprehension''), emotion and valence (e.g., ``amygdala,''
``valance''), or the default mode network (e.g., ``default mode''). The
components we identified were relatively stable across story segments
(Fig.~\synthThirds).

@@

\subsection*{Reverse inference}

@@

>>>>

\newcommand{\topics}{S1}
\newcommand{\topicTags}{S2}

@@

In addition to examining different networks in isolation, we wondered about the
general structure of the full-brain (i.e., potentially multi-network) activity
patterns reflected by different principal components across different
experimental conditions. As shown in Figure~\ref{fig:neurosynth-pca}, we used
Neurosynth~\citep{RubiEtal17} to identify, for each component, the associations
with each of 80 themes (see \textit{Reverse inference}).  In general, the first
principal components across all of the experimental conditions tended to weight
most heavily on themes related to cognitive control, memory,
language processing, attention, and perception.  Other components appeared to
vary more across conditions.

To gain further insights into which brain functions might be most closely
associated with the top-weighted components from each experimental condition,
we manually grouped each Neurosynth-derived topic into a smaller set of core
cognitive functions. Separately for each component, we computed the average
weightings across all topics that were tagged as being associated with each of
these cognitive functions (Figs.~\ref{fig:neurosynth-summary}A,~\neurosynthFull
A). To help visualize these associations, we used the patterns of associations
for each component to construct graphs whose nodes were experimental conditions
and cognitive functions (Figs.~\ref{fig:neurosynth-summary}B,~\neurosynthFull
B). We also computed correlations between the sets of per-topic weightings from
each of the top-weighted components from each experimental condition
(Fig.~\ref{fig:neurosynth-summary}C, D) and between the brain maps for each
condition's components (Fig.~\neurosynthFull C, D). Taken together, we found
that each component appeared to weight on a fundamental set of cognitive
functions that varied by experimental condition. For example, the top principal
components from every condition weighted similarly on the full set of
Neurosynth topics (Fig.~\ref{fig:neurosynth-pca}A) and cognitive functions
(Figs.~\ref{fig:neurosynth-summary}A, B and~\neurosynthFull~A, B), suggesting
that these components might reflect a set of functions or activity patterns
that are common across all conditions. The second components' weightings were
similar across the intact, paragraph, and rest conditions (highest-weighted
functions: cognitive control, memory, social cognition, and resting state), but
different for the word condition (highest-weighted functions: sensory
perception and cognitive control). The fourth components' weighting were
grouped the paragraph and word conditions (highest-weighted functions: memory,
language processing, and cognitive control) and the intact and rest conditions
(highest-weighted functions: emotion, social cognition). We also used
ChatGPT~\citep{ChatGPT} to sort the list of manually tagged cognitive functions
from lowest-level to highest-level (Tab.~\topicTags,
Fig.~\ref{fig:neurosynth-summary}E; also see \textit{Ranking cognititive
processes}). We found that higher-level functions tended to be weighted on more
heavily by top components from the intact and paragraph conditions than
lower-level functions. The top components from the word condition showed the
opposite tendancy, whereby \textit{lower}-level functions tended to be weighted
on more heavily than higher-level functions. The components from the rest
condition showed almost no differences in the weights associated with
high-level versus low-level functions.

@@

\textbf{JRM NOTE: UPDATE THE NEXT TWO SUB-SECTIONS}
\subsection*{Reverse inference}

@@

\subsection*{Ranking cognitive processes}
